Unprepared colonoscopy identifies microbiota specific to the proximal and distal

### 2017-07-27 submission/manuscript.Rmd
code tweaks to make it run

```{r oncogenic_otus, echo=FALSE}
subsampled_meta <- merge(meta_file, subsampled_file, by.x='group', by.y='row.names')
fuso179 <- subsampled_meta[, colnames(subsampled_meta) %in% c("group", "patient", "location", "Otu00179")]
subsampled_to = 4231

@@

p_152 <-subsampled_meta[, colnames(shared_meta) %in% c("Group", "patient", "location", "Otu00152")]

p_152[,4] <- (p_152[,3]/subsampled_to) *100
names(p_152)[4] <- "Otu152_abund"

>>>>

```{r oncogenic_otus, echo=FALSE}
subsampled_meta <- merge(meta_file, subsample, by.x='group', by.y='row.names')
fuso179 <- subsampled_meta[, colnames(subsampled_meta) %in% c("group", "patient", "location", "Otu00179")]
subsampled_to = 4231

@@

p_152 <-subsampled_meta[, colnames(subsampled_meta) %in% c("Group", "patient", "location", "Otu00152")]

p_152[,5] <- (p_152[,4]/subsampled_to) *100
names(p_152)[5] <- "Otu152_abund"
